\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-14 article.tex
Fix naming

\font\myfont=cmr12 at 24pt
\title{\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64}
\author{William Welle Tange, 201809080}

@@

\section*{Acknowledgments}
I would like to express my gratitude and thanks towards all who have facilitated me in making this project a part of reality.
First of all, I can hardly begin to express my gratitude towards my advisors Aslan and Amin for the weekly meetings where most if not all of my confusion was settled.
%Firstly, we would like to thank Bas Spitters, our supervisor, for his guidance and expertise on the subject, as
%well as giving us the idea for the project. Without him this project would not have been possible. Secondly,
%we thank Franziskus Kiefer for his helpfulness in answering questions about various Hacspec-related quirks,
%issues, as well as being swift in these responses despite his large workload. Thirdly, we want to thank Las
%Safin, who helped proofreading and thus make this report more bulletproof. Finally, we thank everyone who
%helped answer questions over the various stages of the project. Your assistance is greatly appreciated
\newpage

@@

One particularly nasty oversight that was discovered a couple of days prior to handin stems from phi movs overwriting each other.
Consider Figure \ref{fig:sqrt1.ll} where two phi instructions either move \texttt{\%6} to \texttt{label \%10} or \texttt{\%7} to \texttt{label \%5} depending on the condition. In some cases, even in greedy where each variable is assigned their own discrete register, their respective values are overwritten. This is due to \texttt{\%7} being moved to \texttt{\%6} prior to potentially branching back to \texttt{label \%5}. If phi moves are conducted unconditionally of branch condition \texttt{\%9}, the value of \texttt{\%6} prior to branching to \texttt{label \%10} is overwritten on the off-chance of returning to \texttt{label \%5}, causing the value assigned to \texttt{\%11} and returned on line 10 to always be equal to \texttt{\%7} instead of the intended \texttt{\%7} instead of the intended  \texttt{\%6}.

>>>>

\font\myfont=cmr12 at 24pt
\title{\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64}
\author{William Welle Tange -- 201809080\\
  Advisors: Aslan Askarov \& Amin Timany
}

@@

\section*{Acknowledgments}
I would like to express my sincere gratitude and thanks to all who have supported me in making this project a part of reality.
First of all, I can hardly begin to express my gratitude towards my advisors Aslan and Amin for the weekly meetings where most if not all concerns were settled.
%Firstly, we would like to thank Bas Spitters, our supervisor, for his guidance and expertise on the subject, as
%well as giving us the idea for the project. Without him this project would not have been possible. Secondly,
%we thank Franziskus Kiefer for his helpfulness in answering questions about various Hacspec-related quirks,
%issues, as well as being swift in these responses despite his large workload. Thirdly, we want to thank Las
%Safin, who helped proofreading and thus make this report more bulletproof. Finally, we thank everyone who
%helped answer questions over the various stages of the project. Your assistance is greatly appreciated
\newpage

@@

One particularly nasty oversight that was discovered a couple of days prior to handin stems from phi movs overwriting each other.
Consider Figure \ref{fig:sqrt1.ll} where two phi instructions either move \texttt{\%6} to \texttt{label \%10} or \texttt{\%7} to \texttt{label \%5} depending on the condition. In some cases, even in greedy where each variable is assigned their own discrete register, their respective values are overwritten. This is due to \texttt{\%7} being moved to \texttt{\%6} prior to potentially branching back to \texttt{label \%5}. If phi moves are conducted unconditionally of branch condition \texttt{\%9}, the value of \texttt{\%6} prior to branching to \texttt{label \%10} is overwritten on the off-chance of returning to \texttt{label \%5}, causing the value assigned to \texttt{\%11} and returned on line 10 to always be equal to \texttt{\%7}   instead of the intended  \texttt{\%6}.
